---
title: "Linear Model"
author: "Evelyn Sanchez"
date: "23 October 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
myData = read.csv('rawData.csv')
```

$H_0$: No difference in the models  
$H_A$: There is a difference in the models

# First model:
SIMS is a function of ARM

```{r}
model1 = lm(SIMS~ARM, data=myData)
summary(model1)
```

predict SIMS for ARM = 88

```{r}
x = data.frame(GRIP=94, ARM=88)
predSIMS1 = predict.lm(model1,x)
print(predSIMS1)
```

prediction interval:

```{r}
predict(model1, x,interval= 'predict')
```


# Second model:

SIMS is a function of GRIP

```{r}
model2 = lm(SIMS~GRIP, data=myData)
summary(model2)
```

predict SIMS for GRIP = 94

```{r}
predSIMS2 = predict.lm(model2,x)
print(predSIMS2)
```

prediction interval:

```{r}
predict(model2, x,interval= 'predict')
```


# Third model:

SIMS is a prediction of ARMS and GRIP

```{r}
model3 = lm(SIMS~ARM+GRIP, data=myData)
summary(model3)
```

predict SIMS for ARM=88 and GRIP=94

```{r}
predSIMS3 = predict.lm(model3,x)
print(predSIMS3)
```

prediction interval:

```{r}
predict(model3, x,interval= 'predict')
```

comparison between models 1 and 3

```{r}
anova(model1,model3)
```

# Conclusion:
 
Since the p-value = 4.994e-06, we reject the null hypothesis.There is a difference between model 1 and model 3 because the p-value < 0.05%. The residual sums of model squares from model 1 is less than the residual model squares from model 3. This means that model 3 is a much better fit.
